The K2 Bright Star Survey

### 2019-05-16 paper/ms.tex
names of red giant stars'

% intro kepler
The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler the exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and these saturated stars were intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry or high-resolution spectroscopy, and they typically have long histories of previous observations.

@@

@@

% how well did we do?
\textcolor{red}{How well do we do? How do we quantify our lightcurve SNR?}

>>>>

% intro kepler
The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler the exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and these saturated stars were intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry or high-resolution spectroscopy, and they typically have long histories of previous observations. Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision lightcurves.

@@

We now seek to establish the global noise properties of the whole unsaturated sample, and compare these to PDC. We process all~2466 stars with TV-min and $\delta = 10$, using all pixels in the TPF unmasked. Because these stars are so bright and the TPFs so small, in the great majority  of cases we do not expect significant contamination, and this is a way of testing how well the weights assigned by TV-min match the flux distribution over pixels.

@@
